Capstone Movielens Report

### 2025-09-28 reports/capstone-movielens.site/02.8-1.MF.UMGYDE-model.Rmd

::: { #func.mf.residual.dataframe.params.description .sidebar }
##### Description
\

@@

::: { #func.mf.residual.dataframe.params.train_set .sidebar }
The dataset to be trained.
:::

@@

A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.params.description) above for the details).

@@

This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.params.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.

##### Parameters
\

::: { #func.UMGYDE_model.predict.params.test_set .sidebar }
###### ***test_set***
\

>>>>

::: { #func.mf.residual.dataframe.args.description .sidebar }
##### Description
\

@@

::: { #func.mf.residual.dataframe.args.train_set .sidebar }
The dataset to be trained.
:::

@@

A data frame object containing the residuals (see the [Description](#func.mf.residual.dataframe.args.description) above for the details).

@@

This is a wrapper for the [UMGY_SmoothedDay_effect.predict](#func.UMGY_SmoothedDay_effect.predict) function described in the [UMGYDE Model: Helper Functions] section above with the fixed [day_smoothed_effect](#func.UMGY_SmoothedDay_effect.predict.args.day_smoothed_effect) parameter value obtained after the _UMGYDE Model_ (described in the [User+Movie+Genre+Year+Day Effect (UMGYDE) Model] section)  has been fully trained.

##### Arguments
\

::: { #func.UMGYDE_model.predict.args.test_set .sidebar }
###### ***test_set***
\
